---
title: "**IntMC**"
subtitle: "**Int**egration of **M**etabolome with **C**linical Data "
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
    highlight: kate
    self_contained: true
    code_folding: hide
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
runtime: shiny
bibliography: reference.bib
csl: springer-vancouver.csl
nocite: '@*'


---


```{r Librerias, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

if(!require("pacman")){install.packages("pacman"); library("pacman")}

librerias <- c("BiocManager", "dplyr","rsconnect", "shiny",
               "ggplot2", "tidyverse", "tidyr", "flexdashboard",
               "ggpubr","dendextend", "MASS", "plotly","ggdendro",
               "knitr", "mixOmics", "FactoMineR","DT",
               "factoextra","shinyWidgets",
               "ggpubr","plyr")


p_load(char = librerias)

options(repos = BiocManager::repositories())
options("repos")

options(shiny.maxRequestSize=40*1024^2)    # equivale a 40MB upload

```

# Overview

-----

<div class=text-justify>

&nbsp;&nbsp;&nbsp;
Metabolomics has immense potential for early diagnosis and monitoring of therapy and for understanding the pathogenesis of many diseases [@jove_plasma_2017; @zhao_liquid_2018; @dougan_metabolomic_2018; @wei_metabolomics_2013; @righi_metabolomic_2020]. We perceived that it is possible to integrate the results of analytical techniques that study the metabolome with clinical information from patients and not only provide insights into trends and data quality, but also formulate hypotheses and make assumptions with applicability in translational, clinical and diagnostic research.


&nbsp;&nbsp;&nbsp;
On this basis, we developed **IntMC, a tool that integrates the results of the analytical techniques of the metabolome with the clinical characteristics of patients in a dynamic, reproducible and simple way**. Integration is achieved with supervised and unsupervised machine learning techniques.

</div>


# IntMC {.tabset .tabset-fade}

---------


## Use

<div class=text-justify>

&nbsp;&nbsp;&nbsp;
Although it is quite intuitive

&nbsp;&nbsp;&nbsp;
**IntMC** Needs:
 
a) From loaded data

b) Perform the selection of clinical variables


&nbsp;&nbsp;&nbsp;
**IntMC** Delivery:

a) Machine learning analytics

b) New groupings if interested

</div>


## Explaining what you Need


<div class=text-justify>


1. The spectrometry/spectroscopy data with the following organization:

   + Rows as samples and columns as features (ions, m/z, compounds).
  
   + The first column will be sample identification (Sample).

2. Clinical data:

   + Rows as the samples and columns as parameters of diagnosis, treatment, etc. (always categorical variables).

   + The first column will be sample identification (Sample).

  3. The first column of spectrum data and clinical data has to match in identification.

  4. Declaration: data is loaded independently, selection of clinical variables is one by one, spectrum range responds to particular types of metabolites

</div>


## Explaining what we Deliver

<div class=text-justify>


1. Four analyzes [@gu_principal_2011; @le_cao_sparse_2011; @ruiz-perez_so_2020]:
  
   + **PCA**: _Principal Component Analysis_ is an unsupervised technique of dimensionality reduction as a function of the original variance of the data.
  
   + **PLS-DA**: _Partial Least Squares Regression-Discriminant Analysis_ is a supervised technique of dimensionality reduction as a function of covariance between the original data and its tags.
  
    + **Hierarchical Cluster**: grouping built with an agglomerative strategy to detect entities with similar characteristics, we use the Euclidean distance and as a linking criterion the one proposed by Ward.

2. Have the possibility to create new groups according to various clinical characteristics and obtain the spectrum for samples

</div>




# Try our test data

-----


<div class=text-justify>

&nbsp;&nbsp;&nbsp;
You can check the data format by downloading the tables below, which also allow you to test the application.


```{r Download-Examples, context = 'server', echo = FALSE}

c18 <- read.table("Data/C18_Negative.csv",
                  sep=",",
                  header = TRUE)
names(c18) <- gsub("X","", names(c18))


clinical <- read.table("Data/Dados_Clinicos.csv",
                  sep=",",
                  header = TRUE)
clinical <- clinical[c(1:80),] 
names(clinical) <- gsub("X","", names(clinical))


wellPanel(

      # Input: Choose dataset ----
      selectInput("dataset", "Data Examples for Download:",
                  choices = c("Mass Spectra", "Clinical Data")),

      # Button
      downloadButton("downloadData", "Download"),
      
      h5(strong(
        #"Sample Data Visualization"
        )),
        
      dataTableOutput('table')

)


datasetInput <- reactive({
    switch(input$dataset,
           "Mass Spectra" = c18,
           "Clinical Data" = clinical)
  })


output$table <- renderDT({

  # DT::datatable(datasetInput(),
  #           extensions = c('FixedColumns'),
  #           options = list(pageLength = 10,
  #                     dom = 'lti',
  #           columnDefs = list(
  #                        list(className = 'dt-center', targets = "_all")),
  #           fixedColumns = list(leftColumns = 1),
  #           scrollX = TRUE
  #           ),
  #           rownames = FALSE
  #)

})


# renderTable({
# 
#     datasetInput()
# 
# })


output$downloadData <- downloadHandler(
    filename = function() {
      paste(input$dataset,".csv")
    },
    content = function(file) {
      write.table(datasetInput(), file, 
                sep=",",
                quote = FALSE,
                col.names = TRUE,
                row.names = FALSE)
    }
  )

```

```
NOTE: Note that you can input spectral data with and without pre-processing (transformation, normalization, scaling, etc). But remember, if you build a new grouping mixing different clinical variables, the change in the number of patients forces you to reproduce the pre-processing if you have done so. Another point, despite the fact that the selection of variables is unique, it can respond to groupings obtained by different clinical characteristics.
```

</div>



# Let's go...

---------


## A. Load Data


```{r Carregar-Dados-UI, echo=FALSE}

  splitLayout(
    
    fileInput("file1", "Mass Spectra",
                    multiple = TRUE,
                    accept = c("text/csv",
                             "text/comma-separated-values,text/plain",
                             ".csv")),
    fileInput("file2", "Clinical Data",
                    multiple = TRUE,
                    accept = c("text/csv",
                             "text/comma-separated-values,text/plain",
                             ".csv")))

    splitLayout(
    verticalLayout(  
    checkboxInput('header1', 'Header', TRUE),
    checkboxInput('ionsid', 'rt_mz', TRUE)),
    radioButtons('sep1', 'Separator',
                             c("Tab"='\t',
                               "Comma"=',',
                               "Semicolon"=';'),
                                selected = c("Tab")),
    checkboxInput('header2', 'Header', TRUE),
    radioButtons('sep2', 'Separator',
                             c("Tab"='\t',
                               "Comma"=',',
                               "Semicolon"=';'),
                                selected = c("Tab"))
               )

  
  

```



```{r Carregar Dados-Server, echo=FALSE}

mass.sp <- reactive({

          inFile <- input$file1

          if (is.null(inFile))
            return(NULL)

            read.table(inFile$datapath,
                                dec = ".",
                                sep = input$sep1,
                                header = input$header1,
                                stringsAsFactors = FALSE)

})



clinical.dat <- reactive({

          inFile <- input$file2

          if (is.null(inFile))
            
            return(NULL)

            read.table(inFile$datapath,
                                dec = ".",
                                sep = input$sep2,
                                header = input$header2,
                                stringsAsFactors = FALSE)

})



renderPrint({

HTML("The data has ", nrow(mass.sp()), "samples and", ncol(mass.sp())-1, " features(m/z).
  
The samples are described by", ncol(clinical.dat())-1, "clinical characteristics")

})


```


```{r Intervalo Features, echo = FALSE}

# Importante para a seleção das features

category <- reactive({
  
    inFile <- input$file2
 
    if (is.null(inFile))({
    
    E <- return(paste0("No file selected"))
        
    }) else({
      
    E <- levels(as.factor(names(clinical.dat())[2:ncol(clinical.dat())]))
      
    })

  D <- c("None", E)

})



aux1 <- reactive({

        if (input$ionsid == TRUE) {
        
          aux1 <- data.frame(
                    Features= names(mass.sp())[2:ncol(mass.sp())],
                    Ions= names(mass.sp())[2:ncol(mass.sp())]
                    )
            
          aux1 <- separate(data = aux1,
                           col = Ions,
                           into=c("tempo", "ions"),
                           sep = "_")
        
            aux1$Features <- gsub("X","", aux1$Features)
            aux1$ions <- gsub("m.z","", aux1$ions)
            aux1$ions <- gsub("n","", aux1$ions)
            aux1$ions <- as.numeric(aux1$ions)
  
} else {
  
            aux1 <- data.frame(
            ions= names(mass.sp())[2:ncol(mass.sp())])
            
            aux1$ions <- gsub("X","", aux1$ions)
            aux1$ions <- as.numeric(aux1$ions)
  
}
    

aux1

})


```



## B. Variable Selection


<div class=text-justify>

&nbsp;&nbsp;&nbsp;

Consider that when studying a range of spectra you may be focusing on specific types of metabolites. The first approach does not include any clinical variables, only spectral values will be used for groupings.

</div>


```{r Leer Variaveis}

renderUI({

wellPanel(

fluidRow(
    column(6,
           sliderInput(inputId = "espectro",
            label = "Spectrum Range: ",
             min = 50,
             max = 1700,
             value = c(400,1000),
            step=50)),
    column(6,
           selectInput("var", "Clinical variables: ",
                       choices = category(),
                       selected= category()[1],
                       multiple = FALSE))
    )
      
)
           
})
  
# Valores da janela deslizante

values.espectro <- reactive({

data.frame(
        Name = c("Minimo","Maximo"),
        Range = as.numeric(input$espectro),
        stringsAsFactors = FALSE )

})


# Resumo do trabalho do usuário

renderPrint({

HTML("Is grouping the data according to the variable", input$var,".
  
In the spectrum range of", paste(input$espectro, collapse="~"), "m/z.")

})


```



```{r Unir Variavel, echo= FALSE}

# Unir os dados espectrales e clinicos

data <- reactive({
  aux1 <- inner_join(clinical.dat(), mass.sp(), by = "Sample")
  names(aux1) <- gsub("X","", names(aux1))
  aux1
})


### Esta aqui o NOSSO PROBLEMA. Como definar o menor e maios

set  <- reactive({

  aux2 <- subset(aux1(), aux1()$ions <= values.espectro()[2,2] &
                   aux1()$ions >= values.espectro()[1,2])


  aux3 <- data()[,names(data()) %in% aux2[,1]]
  
  aux4 <- data.frame(data()[,1:length(category())], aux3)
  
  names(aux4) <- gsub("X","", names(aux4))
   
  aux4


})



```



##  C. Analysis


```{r Analises , warning= FALSE, message= FALSE,error=FALSE, echo = FALSE}

# # Painel que mostra as analises que estão implementadas

tabsetPanel(type = "tabs",
               tabPanel("PCA", 
                        plotlyOutput("pca")),
               tabPanel("PLS-DA",
                        plotlyOutput("plsda")),
               #tabPanel("Volcano Plot",plotOutput("volcano")),
               tabPanel("Hierarchical Cluster",
                        plotlyOutput("clustering"))

            )

# seleção de Variaveis
b <- reactive({
  
   N <- length(category())
  
   N <- N+1
   
   B <- set()[,c(which(names(set())==input$var), 
                 N:ncol(set()))]
  
   B

})


# PCA
 
pca.exp <- reactive ({
  
  pca(as.matrix(b()[,2:ncol(b())]),
      ncomp=3,
      center = TRUE,
      scale= TRUE)
  


})
 
output$pca <- renderPlotly({
   
p <- plotIndiv(pca.exp(),
          group = b()[,1],
          pch=as.factor(b()[,1]),
          legend = TRUE,
          title = paste0("PCA ", input$var)
          )

df <- p$df

Patients <- gsub("_.*","", set()[,1])
Patients <- gsub("^","Sample: ", Patients)

f <- ggplot(df, aes(x,
                    y,
                    color= group,
                    group= Patients,
                    text = Patients)) +
  geom_point(pch=df$pch, size=df$cex) +
  labs(title = levels(df$Block),
       x = p[["graph"]][["labels"]][["x"]],
       y = p[["graph"]][["labels"]][["y"]]) +
  theme_test() +
  theme(legend.position="bottom",legend.title=element_blank())+
  geom_hline(yintercept = 0,linetype = "dashed", color="lightgray") +
  geom_vline(xintercept = 0, linetype = "dashed", color="lightgray")

ggplotly(f,tooltip = "text")


})


# PLS-DA


plsda.exp <- reactive({

  plsda (b()[,2:ncol(b())],
         as.factor(b()[,1]),
         ncomp= 3,
         scale= TRUE,
         mode= "regression")


})



output$plsda <- renderPlotly({

p <- plotIndiv(plsda.exp(),
            group = b()[,1],
            pch=as.factor(b()[,1]),
            legend = TRUE,
            title = paste0("PLS-DA ", input$var)
            )

df <- p$df

Patients <- gsub("_.*","", set()[,1])
Patients <- gsub("^","Sample: ", Patients)

f <- ggplot(df, aes(x,
                    y,
                    color= group,
                    group= Patients,
                    text = Patients)) +
  geom_point(pch=df$pch, size=df$cex) +
  labs(title = levels(df$Block),
       x = p[["graph"]][["labels"]][["x"]],
       y = p[["graph"]][["labels"]][["y"]]) +
  theme_test() +
  theme(legend.position="bottom",legend.title=element_blank())+
  geom_hline(yintercept = 0,linetype = "dashed", color="lightgray") +
  geom_vline(xintercept = 0, linetype = "dashed", color="lightgray")

ggplotly(f,tooltip = "text")


})

# Volcano plot

# volcano.exp <- reactive({
# 
#   G0 <- as.data.frame(table(b()[,1]))
#   G1 <- G0[1,1]
#   G2 <- G0[2,1]
# 
# g <- NULL
#        for (i in 2:ncol(b())) {
#          AG <- which(b()[,1] == G1)
#          BG <- which(b()[,1] == G2)
# 
#          median.AG <- median(b()[which(b()[,1] == G1),i])
#          median.BG <- median(b()[which(b()[,1] == G2),i])
#          fold.change <- median.AG/median.BG
#          log2FC <- log2(fold.change)
# 
#          wilcox <- wilcox.test(b()[which(b()[,1] == G1),i],
#                                b()[which(b()[,1] == G2),i])$p.value
# 
#          f <- cbind (median.AG,
#                      median.BG,
#                      fold.change,
#                      log2FC,
#                      wilcox)
# 
#          g <- rbind(g,f)
# 
#        }
# 
#        p <- data.frame(g)
#        M <- names(b())[2:ncol(b())]
#        rownames(p) <- M
#        p <- data.frame(Compound=rownames(p),p)
#        rownames(p) <- NULL
#        names(p)[c(2,3)] <- c(as.character(G1),
#                              as.character(G2))
#        p_values_BH <- p.adjust(p = p$wilcox, method = "BH")
#        p <- data.frame(p, p.adjust=p_values_BH)
#        p$Compound <- gsub("X","",p$Compound)
# 
#  p
# 
# })
#  
#  
# output$volcano <- renderPlot({
# 
# ggplot(volcano.exp(),aes(x=log2FC, y=-log2(wilcox))) +
#           geom_point()+
#           theme_test() +
#           labs(title = paste0("Volcano plot ",
#                               input$var, "  ",
#                               names(volcano.exp())[2], " vs ",
#                               names(volcano.exp())[3]))+
#           xlab ("log2(FC)") +
#           ylab (" -log2(p-value)") +
#           geom_hline(yintercept = -log2(0.05),
#                      linetype = "dashed", color="lightgray")+
#           geom_vline(xintercept =  log2(2),
#                      linetype = "dashed", color="lightgray")+
#           geom_vline(xintercept = - log2(2), linetype = "dashed",
#                      color="lightgray")+
#           scale_x_continuous(limits = c(-3, 3),breaks = c(-1,0,1))+
#           scale_y_continuous(limits = c(0, 8),breaks = c(0,4.32))
# 
# })


# Clustering

clustering.exp <- reactive ({

                set.seed(1234)
                group <- hclust(dist(b()[,-1], method = 'euclidean'),
                                method = 'ward.D')
                dend <- as.dendrogram(group)
                dend_data <- dendro_data(dend, type = "rectangle")
dend_data

})

output$clustering <- renderPlotly({

Patients <- gsub("_.*","", set()[,1])
Patients <- gsub("^","Sample: ", Patients)

  
clust<- ggplot(clustering.exp()$segments) +
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) +
              labs(x="",
                   y="Heigth",
                   title = paste0("Clustering ",
                              input$var),
                   color = input$var) +
              coord_flip()+
              scale_y_reverse() +
              geom_point(data =clustering.exp()$labels,
                  aes(x = x,
                      y =y,
                      label = b()[clustering.exp()$labels$label,1],
                      text = Patients,
              colour = as.factor(b()[clustering.exp()$labels$label,1])),
                  hjust =1, angle = 0, size =1)+
              theme_test() +
              theme(legend.position = "bottom")

ggplotly(clust, tooltip = "text")

})


g <- reactive({

  g <- data.frame(table(b()[,1]))
  names(g) <- c(paste0("Category-",input$var),
                "Amount")

  g

})


renderDataTable({
  datatable(g(), rownames = FALSE,options = list(dom = 't'))

  })


```


## D. New groups


<div class=text-justify>

&nbsp;&nbsp;&nbsp;
We understand that it could be interesting to explore how the separation of patients occurs if we carry out groupings based on more than one clinical characteristic. To support the user in this task we developed this section in which he will be free to form new datasets. When changing the configuration of the groups, we provide tools for downloading clinical and spectral data separately so that they can be analyzed again by this tool. Remember that if the pre-processing of data was carried out before the formation of these new groups, they must undergo pre-processing. 

</div>


```{r Ajuda-UI, echo = FALSE}


renderUI({
  
  
  
tabsetPanel(
    
    tabPanel("Selection",
# Variavies clinicas             
             fluidRow(
                      column(3,
                             selectInput("clinica1", "Clinical variables 1: ",
                                         choices = categoria1(),
                                         selected= categoria1()[1],
                                         multiple = FALSE)),
                      column(3,
                             selectInput("clinica2", "Clinical variables 2: ",
                                         choices = categoria2(),
                                         selected= categoria2()[1],
                                         multiple = FALSE)), 
                      column(3,
                             selectInput("clinica3", "Clinical variables 3: ",
                                         choices = categoria3(),
                                         selected= categoria3()[1],
                                         multiple = FALSE)),
                      column(3,
                             selectInput("clinica4", "Clinical variables 4: ",
                                         choices = categoria4(),
                                         selected= categoria4()[1],
                                         multiple = FALSE))
             ),

# Categorias de variaveis             
renderUI({
             fluidRow(
                      column(3,
                             selectInput("cat1", "Category: ",
                                         choices = value1(),
                                         selected= value1()[1],
                                         multiple = FALSE)),
                      column(3,
                             selectInput("cat2", "Category: ",
                                         choices = value2(),
                                         selected= value2()[1],
                                         multiple = FALSE)),
                      column(3,
                             selectInput("cat3", "Category: ",
                                         choices = value3(),
                                         selected= value3()[1],
                                         multiple = FALSE)),
                      column(3,
                             selectInput("cat4", "Category: ",
                                         choices = value4(),
                                         selected= value4()[1],
                                         multiple = FALSE))
             )
        }),

textOutput("resumo"),
   
wellPanel(
    
  fluidRow(
    column(6,
     selectInput("filter.spectrum", "Mass Spectra: ",
                    choices = c("Filtered Mass Spectra")),
     downloadButton("downloadData1", "Download")),
    column(6,
     selectInput("filter.clinic", "Clinical Data:",
                    choices = c("Filtered Clinical Data")),
     downloadButton("downloadData2", "Download"))
          )
      )
          )
    
    
    )


  
})


```



```{r Ajuda-Identifação de variavies, echo=FALSE}

# Variaveis Clinicas

categoria1 <- reactive({
  
    inFile <- input$file2
 
    if (is.null(inFile))({
    
    E <- return(paste0("No file selected"))
        
    }) else({
      
    E <- levels(as.factor(names(clinical.dat())[2:ncol(clinical.dat())]))
      
    })

  D <- c("None", E)

})



categoria2 <- reactive({
  
    inFile <- input$file2
 
    if (is.null(inFile))({
    
    E <- return(paste0("No file selected"))
        
    }) else({
      
    E <- levels(as.factor(names(clinical.dat())[2:ncol(clinical.dat())]))
      
    })

  D <- c("None", E)

})


categoria3 <- reactive({
  
    inFile <- input$file2
 
    if (is.null(inFile))({
    
    E <- return(paste0("No file selected"))
        
    }) else({
      
    E <- levels(as.factor(names(clinical.dat())[2:ncol(clinical.dat())]))
      
    })

  D <- c("None", E)

})



categoria4 <- reactive({
  
    inFile <- input$file2
 
    if (is.null(inFile))({
    
    E <- return(paste0("No file selected"))
        
    }) else({
      
    E <- levels(as.factor(names(clinical.dat())[2:ncol(clinical.dat())]))
      
    })

  D <- c("None", E)

})


# Valores das Variaveis

value1 <- reactive({
  
 Y <- data.frame(Sample = clinical.dat()[,1],
            Value= clinical.dat()[, which(names(clinical.dat())==input$clinica1)])
 Y <- as.character(unique(Y$Value))
 Y <- c("None", Y)
 Y
})


value2 <- reactive({
  
 Y <- data.frame(Sample = clinical.dat()[,1],
            Value= clinical.dat()[, which(names(clinical.dat())==input$clinica2)])
 Y <- as.character(unique(Y$Value))
 Y <- c("None", Y)
 Y
})


value3 <- reactive({
  
 Y <- data.frame(Sample = clinical.dat()[,1],
            Value= clinical.dat()[, which(names(clinical.dat())==input$clinica3)])
 Y <- as.character(unique(Y$Value))
 Y <- c("None", Y)
 Y
})



value4 <- reactive({
  
 Y <- data.frame(Sample = clinical.dat()[,1],
            Value= clinical.dat()[, which(names(clinical.dat())==input$clinica4)])
 Y <- as.character(unique(Y$Value))
 Y <- c("None", Y)
 Y
})



```


```{r Seleção-Variaveis, echo=FALSE}


H <- reactive({
  
  H <- data.frame(Sample = clinical.dat()[,1],
                  Value= clinical.dat()[, 
                    c(which(names(clinical.dat())==input$clinica1),
                      which(names(clinical.dat())==input$clinica2),
                      which(names(clinical.dat())==input$clinica3),                                             which(names(clinical.dat())==input$clinica4))])
  H
  
})



J <- reactive({

  if(input$cat1 != "None"){

    A <- data.frame(Sample = clinical.dat()[,1],
                    Value= clinical.dat()[,
                    c(which(names(clinical.dat())==input$clinica1))])

    A <- subset(A,A[,2] == input$cat1)

  } else {

    A <-NULL}


 if(input$cat2 != "None"){

    B <- data.frame(Sample = clinical.dat()[,1],
                    Value= clinical.dat()[,
                    c(which(names(clinical.dat())==input$clinica2))])

    B <- subset(B,B[,2] == input$cat2)

  } else {

    B <-NULL}


  if(input$cat3 != "None"){

    C <- data.frame(Sample = clinical.dat()[,1],
                    Value= clinical.dat()[,
                    c(which(names(clinical.dat())==input$clinica3))])

    C <- subset(C,C[,2] == input$cat3)

  } else {

    C <-NULL}


    if(input$cat4 != "None"){

    D <- data.frame(Sample = clinical.dat()[,1],
                    Value= clinical.dat()[,
                    c(which(names(clinical.dat())==input$clinica4))])

    D <- subset(D,D[,2] == input$cat4)

  } else {

    D <-NULL}


  a <- A[,1]
  b <- B[,1]
  c <- C[,1]
  d <- D[,1]
  

  if(!is.null(a)& is.null(b)& is.null(c)& is.null(d))
  {E <- Reduce(intersect, list(a))}

  if(is.null(a)& !is.null(b)& is.null(c)& is.null(d))
  {E <- Reduce(intersect, list(b))}

  if(is.null(a)& is.null(b)& !is.null(c)& is.null(d))
  {E <- Reduce(intersect, list(c))}

  if(is.null(a)& is.null(b) & is.null(c)& !is.null(d))
    {E <- Reduce(intersect, list(d))}

  if(!is.null(a)& !is.null(b)& is.null(c)& is.null(d))
    {E <- Reduce(intersect, list(a,b))}

  if(!is.null(a)&!is.null(c))
    {E <- Reduce(intersect, list(a,c))}

  if(!is.null(a)& is.null(b)& is.null(c)& !is.null(d))
    {E <- Reduce(intersect, list(a,d))}

  if(is.null(a)& !is.null(b)& !is.null(c)& is.null(d))
    {E <- Reduce(intersect, list(b,c))}

  if(!is.null(b)&!is.null(d))
    {E <- Reduce(intersect, list(b,d))}

  if(is.null(a)& is.null(b)& !is.null(c)& !is.null(d))
  {E <- Reduce(intersect, list(c,d))}


  if(!is.null(a)& !is.null(b)& !is.null(c)& is.null(d))
    {E <- Reduce(intersect, list(a,b,c))}

  if(!is.null(a)& !is.null(b)& is.null(c)& !is.null(d))
    {E <- Reduce(intersect, list(a,b,d))}

  if(!is.null(a)& is.null(b)& !is.null(c)& !is.null(d))
    {E <- Reduce(intersect, list(a,c,d))}


  if(!is.null(a) & !is.null(b) & !is.null(c) & !is.null(d))
    {E <- Reduce(intersect, list(a,b,c,d))}
  E


})


clinical.filter <- reactive({

  P <- clinical.dat()[clinical.dat()[,1] %in% J(),]

  P

})


mass.filter <- reactive({

  R <- mass.sp()[mass.sp()[,1] %in% J(),]

  R

})





```


```{r Download-Filtering, echo=FALSE}


# output$resumo <- renderText({
#   
#   paste0("Vamos a escrebir como funciona el classificadaor", )
#   
#   
# })




################################################
dataOutputMass <- reactive({
    switch(input$filter.spectrum,
           "Filtered Mass Spectra" = mass.filter())
  })

output$downloadData1 <- downloadHandler(
    filename = function() {
      paste("Spectrum-Data-Filtering.csv")
    },
    content = function(file) {
      write.csv(dataOutputMass(), file, quote = FALSE, row.names = FALSE)
    }
  )

###########################################################

dataOutputClinical <- reactive({
    switch(input$filter.clinic,
           "Filtered Clinical Data" = clinical.filter())
  })

output$downloadData2 <- downloadHandler(
    filename = function() {
      paste("Clincal-Data-Filtering.csv")
    },
    content = function(file) {
      write.csv(dataOutputClinical(), file, quote = FALSE, row.names = FALSE)
    }
  )


```


# Reference

----

